This is an example of article title

### 2019-06-24 paper/paper.tex
Updates from Overleaf

%%%
%% Fonts and Typewriting
%%%
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{bm}

%%%
%% Enhances Figures and Tables environments
%%%
\usepackage{placeins}
\usepackage[hypcap=true]{caption}
\usepackage{booktabs, multirow, array, tabularx, floatrow, cellspace, threeparttable}
\floatsetup[table]{capposition = top}
\newcolumntype{Z}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\renewcommand{\arraystretch}{1.25}

@@

%%%
%% Cross References
%%%
\usepackage{cleveref}

@@

@@

Software to economists is what hammers are to blacksmiths. As scientists, the tools to work with data are as important as the know-how to perform the analysis. A requirement for good science is that the tools used in the process have a certain standard in terms of quality, transparency, and flexibility. The analysis must allow for the process to be verifiable and replicable.

@@

The Julia language \cite{Julia} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks. The following sections describe commons estimators, the Julia ecosystem supporting tools, and Econometrics.jl which provides further functionality.

\section{The JuliaCon Article Class}
\label{sec:documentclass}
%
The juliacon class file preserves the standard LATEX{} interface such
that any document that can be produced using the standard LATEX{}
article class can also be produced with the class file.\vskip 6pt
It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.\vskip 6pt
Use should be made of symbolic references (\verb \ref ) in order to
protect against late changes of order, etc.

\section{USING THE JuliaCon Article CLASS FILE}

If the file \verb juliacon.cls  is not already in the appropriate system directory
for \LaTeX{} files, either arrange for it to be put there or copy
it to your working directory. The \verb juliacon  document class is implemented
as a complete class, not a document style option. In order to
use the \verb juliacon  document class, replace \verb article  by \verb juliacon  in the
\verb \documentclass  command at the beginning of your document:
\vskip 6pt
\begin{centering}
    \verb \documentclass{article}  \end{centering}
\vskip 6pt
replace by
\vskip 6pt
 \verb \documentclass{juliacon}  \vskip 6pt
In general, the following standard document \verb style  options should
{ \itshape not} be used with the {\footnotesize \itshape article} class file:
\begin{enumerate}
\item[(1)] \verb 10pt,  \verb 11pt,  \verb 12pt   ? unavailable;
\item[(2)] \verb twoside  (no associated style file) ? \verb twoside  is the default;
\item[(3)] \verb fleqn, \verb leqno, \verb titlepage ? should not be used;
\end{enumerate}

\section{Additional Document Style Options}
\label{sec:additional_doc}
%
The following additional style option is available with the \verb juliacon  class file:
\vskip 6pt
Please place any additional command definitions at the very start of
the \LaTeX{} file, before the \verb \begin{document} . For example, user-defined
\verb \def  and \verb \newcommand   commands that define macros for
technical expressions should be placed here. Other author-defined
macros should be kept to a minimum.
\vskip 6pt
Commands that differ from the standard \LaTeX{} interface, or that
are provided in addition to the standard interface, are explained in
this guide. This guide is not a substitute for the \LaTeX{} manual itself.
Authors planning to submit their papers in \LaTeX{} are advised to use
\verb \juliacon.cls  as early as possible in the creation of their files.

%
%
%
%
\begin{table*}[t]
\tabcolsep22pt
\tbl{If necessary, the tables can be extended both columns.}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\label{tab:symbols}
\begin{tabnote}
This is an example of table footnote.
\end{tabnote}
\end{table*}
% \begin{figure*}[t]
% \centerline{\includegraphics[width=11cm]{juliagraphs.png}}
% \caption{If necessary, the images can be extended both columns.}
%   \label{fig:sample_image}
% \end{figure*}

\section{Additional features}
\label{sec:additional_faci}
In addition to all the standard \LaTeX{} design elements, the \verb juliacon  class file includes the following features:
In general, once you have used the additional \verb juliacon.cls facilities
in your document, do not process it with a standard \LaTeX{} class
file.

\subsection{Titles, Author's Name, and Affiliation}
\label{subsub:title_auth}
The title of the article, author's name, and affiliation are used at the
beginning of the article (for the main title). These can be produced
using the following code:

\begin{verbatim}
\title{ This is an example of article title} }
\author{
   \large 1st Author \\[-3pt]
   \normalsize 1st author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	1st author's email address \\[-3pt]
  \and
   \large 2nd Author \\[-3pt]
   \normalsize 2nd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	2nd author's email address \\[-3pt]
\and
   \large 3rd Author \\[-3pt]
   \normalsize 3rd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	3rd author's email address \\[-3pt]
}
\maketitle
\end{verbatim}

\subsection{Writing Julia code}

A special environment is already defined for Julia code,
built on top of \textit{listings} and \textit{jlcode}.

\begin{verbatim}
\begin{lstlisting}[language = Julia]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
\end{verbatim}
\begin{lstlisting}[language = Julia]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}

\subsection{Abstracts, Key words, term etc...}
\label{subsub:abs_key_etc}

At the beginning of your article, the title should be generated
in the usual way using the \verb \maketitle  command. For genaral tem and keywords use
\verb \terms ,
\verb \keywords  commands respectively. The abstract should be enclosed
within an abstract environment, All these environment
can be produced using the following code:
\begin{verbatim}
\terms{Experimentation, Human Factors}

\keywords{Face animation, image-based modelling...}

\begin{abstract}
In this paper, we propose a new method for the
systematic determination of the model's base of
time varying delay system. This method based on
the construction of the classification data related
to the considered system. The number, the orders,
the time delay and the parameters of the local
models are generated automatically without any
knowledge about the full operating range of the
process. The parametric identification of the local
models is realized by a new recursive algorithm for
on line identification of systems with unknown time
delay. The proposed algorithm allows simultaneous
estimation of time delay and parameters of
discrete-time systems. The effectiveness of
the new method has been illustrated through
simulation.
\end{abstract}

\end{verbatim}

\section{Some guidelines}
\label{sec:some_guide}
The following notes may help you achieve the best effects with the
\verb juliacon  class file.

\subsection{Sections}
\label{subsub:sections}
\LaTeXe{}  provides four levels of section headings and they are all
defined in the \verb juliacon  class file:
\begin{itemize}
\item \verb \section   \item \verb \subsection  \item \verb \subsubsection  \item \verb \paragraph  \end{itemize}
Section headings are automatically converted to allcaps style.
\subsection{Lists}
\label{sec:lists}
%
The \verb juliacon   class file provides unnumbered lists using the
\verb unnumlist  environment for example,

\begin{unnumlist}
\item First unnumbered item which has no label and is indented from the
left margin.
\item Second unnumbered item.
\item Third unnumbered item.
\end{unnumlist}
The unnumbered list which has no label and is indented from the
left margin. was produced by:
\begin{verbatim}
\begin{unnumlist}
\item First unnumbered item...
\item Second unnumbered item...
\item Third unnumbered item...
\end{unnumlist}
\end{verbatim}

The \verb juliacon   class file also provides hyphen list using the
\verb itemize  environment for example,
\begin{itemize}
\item First unnumbered bulleted item which has no label and is indented
from the left margin.
\item Second unnumbered bulleted item.
\item Third unnumbered bulleted item which has no label and is indented
from the left margin.
\end{itemize}
was produced by:
\begin{verbatim}
\begin{itemize}
\item First item...
\item Second item...
\item Third item...
\end{itemize}
\end{verbatim}

Numbered list is also provided in acmtog class file using the
enumerate environment for example,
\begin{enumerate}
\item The attenuated and diluted stellar radiation.
\item Scattered radiation, and
\item Reradiation from other grains.
\end{enumerate}

was produced by:
\begin{verbatim}
\begin{enumerate}
\item The attenuated...
\item Scattered radiation, and...
\item Reradiation from other grains...
\end{enumerate}
\end{verbatim}
\subsection{Illustrations (or figures)}
\label{subsub:sec_Illus}
The \verb juliacon   class file will cope with most of the positioning of
your illustrations and you should not normally use the optional positional
qualifiers on the \verb figure   environment that would override
these decisions.
\vskip 6pt

%
\begin{figure}[t]
\centerline{\includegraphics[width=4cm]{juliagraphs.png}}
\caption{This is example of the image in a column.}
	\label{fig:sample_figure}
\end{figure}

The figure \ref{fig:sample_figure} is taken from the JuliaGraphs
organization \footnote{https://github.com/JuliaGraphs}.

Figure captions should be \emph{below} the figure itself, therefore the
\verb \caption  command should appear after the figure or space left for
an illustration. For example, Figure 1 is produced using the following
commands:

\begin{verbatim}
\begin{figure}
\centerline{\includegraphics[width=20pc]{Graphics.eps}}
\caption{An example of the testing process for a
binary tree. The globa null hypothesis is tested
first at level $\alpha$ (a), and the level of
individual variables is reached last (d). Note
that individual hypotheses can be tested at
level $\alpha/4$ and not $\alpha/8$ as one might
expect at first.}
\label{sample-figure_2}
\end{figure}
\end{verbatim}
Figures can be resized using first and second argument of
\verb \includegraphics   command. First argument is used for modifying
figure height and the second argument is used for modifying
figure width respectively.
\vskip 6pt
Cross-referencing of figures, tables, and numbered, displayed
equations using the \verb \label  and \verb \ref   commands is encouraged.
For example, in referencing Figure 1 above, we used
\verb Figure~\ref{sample-figure}   \subsection{Tables}
\label{subsub:sec_Tab}
The \verb juliacon   class file will cope with most of the positioning of
your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
decisions. Table captions should be at the top.
\begin{verbatim}
\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Train70 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test70 & Testing Data I & & 105\\\hline
Test30 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}\end{verbatim}

\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}
\subsection{Landscaping Pages}
\label{subsub:landscaping_pages}
If a table is too wide to fit the standard measure, it may be turned,
with its caption, to 90 degrees. Landscape tables cannot be produced
directly using the \verb juliacon   class file because \TeX{} itself cannot
turn the page, and not all device drivers provide such a facility.
The following procedure can be used to produce such pages.
\vskip 6pt
Use the package \verb rotating   in your document and change the coding
from
\begin{verbatim}
\begin{table}...\end{table}
to
\begin{sidewaystable}...\end{sidewaystable}
and for figures
\begin{figure}...\end{figure}
to
\begin{sidewaysfigure}...\end{sidewaysfigure}
\end{verbatim}

environments in your document to turn your table on the appropriate
page of your document. For instance, the following code prints
a page with the running head, a message half way down and the
table number towards the bottom.
\begin{verbatim}
\begin{sidewaystable}
\tbl{Landscape table caption to go here.}{...}
\label{landtab}
\end{sidewaystable}
\end{verbatim}

\subsection{Double Column Figure and Tables}
\label{subsub:double_fig_tab}
For generating the output of figures and tables in double column
we can use the following coding:

\begin{enumerate}
\item For Figures:
\begin{verbatim}
\begin{figure*}...\end{figure*}
\end{verbatim}
\item For landscape figures:
\begin{verbatim}
\begin{sidewaysfigure*}...\end{sidewaysfigure*}
\end{verbatim}
\item For Tables:
\begin{verbatim}
\begin{table*}...\end{table*}
\end{verbatim}
\item For landscape tables:
\begin{verbatim}
\begin{sidewaystable*}...\end{sidewaystable*}
\end{verbatim}
\end{enumerate}

\subsection{Typesetting Mathematics}
\label{subsub:type_math}
The \verb juliacon class file will set displayed mathematics with center to
the column width, provided that you use the \LaTeXe{} standard of
open and closed square brackets as delimiters.
The equation
\[
\sum_{i=1}^p \lambda_i = (S)
\]

was typeset using the acmtog class file with the commands

\begin{verbatim}
\[
\sum_{i=1}^p \lambda_i = (S)
\]
\end{verbatim}

For display equations, cross-referencing is encouraged. For example,
\begin{verbatim}
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.
\end{verbatim}
The following output is generated with the above coding:
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.

\subsection{Enunciations}
\label{subsub:enunciation}
The \verb juliacon   class file generates the enunciations with the help of
the following commands:
\begin{verbatim}
\begin{theorem}...\end{theorem}
\begin{strategy}...\end{strategy}
\begin{property}...\end{property}
\begin{proposition}...\end{proposition}
\begin{lemma}...\end{lemma}
\begin{example}...\end{example}
\begin{proof}...\end{proof}
\begin{definition}...\end{definition}
\begin{algorithm}...\end{algorithm}
\begin{remark}...\end{remark}
\end{verbatim}
The above-mentioned coding can also include optional arguments
such as
\begin{verbatim}
\begin{theorem}[...]. Example for theorem:
\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven ... created equal.
\end{theorem}
\end{verbatim}

\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven years ago our fathers brought forth,
upon this continent, a new nation, conceived in Liberty,
 and dedicated to the proposition that all men are
created equal.
\end{theorem}

\subsection{Extract}
\label{subsub:extract}
Extract environment should be coded within
\begin{verbatim}
\begin{extract}..\end{extract}
\end{verbatim}

\subsection{Balancing column at last page}
\label{subsub:Balance}
For balancing the both column length at last page use :
\begin{verbatim}
\vadjust{\vfill\pagebreak}
\end{verbatim}

%\vadjust{\vfill\pagebreak}

at appropriate place in your \TeX{} file or in bibliography file.

\section{Handling references}
\label{subsub:references}
References are most easily (and correctly) generated using the
BIBTEX, which is easily invoked via
\begin{verbatim}
\bibliographystyle{juliacon}
\bibliography{ref}
\end{verbatim}
When submitting the document source (.tex) file to external
parties, the ref.bib file should be sent with it.
\cite{bezanson2017julia}

>>>>

%%%
%% Fonts and Typewriting
%%%
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{bm}
\usepackage{microtype}

%%%
%% Enhances Figures and Tables environments
%%%
\usepackage{placeins}
\usepackage[hypcap=true]{caption}
%\captionsetup[table]{labelfont=bf,textfont=it}
%\captionsetup[figure]{labelfont=bf,textfont=it}
\usepackage{booktabs, multirow, array, tabularx, floatrow, cellspace, threeparttable}
\floatsetup[table]{capposition = top}
\newcolumntype{Z}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\renewcommand{\arraystretch}{1.25}

@@

@@

% An abstract with at most 600 characters, written in plain English with no symbol nor formula.
% A list of at most 10 keywords as specified in the template, separated by commas and written in plain English.
% Compared to an extended abstract, a full paper presents more of the background and context motivating the work. It compares the work to other approaches taken in the field and gives some additional insights on the talk. Use cases back up the work by showing how it can be used.

@@

@@

The Julia language \cite{Bezanson_Edelman_Karpinski_Shah_2017} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks. The following sections describe commons estimators, the Julia ecosystem supporting tools, and Econometrics.jl which provides further functionality.

\section{Common Estimators}

\subsection{Weighted Least Squares}

Weighted least squares solves

\begin{equation}
	\beta = \left(X^{\top} W X\right)^{-1} X^{\top} W y
\end{equation}
with information matrix
\begin{equation}
\Psi = \left(X^{\top} W X\right)^{-1}
\end{equation}

where $X$ is the full rank version of a model matrix, $W$ a diagonal matrix with positive values (e.g., frequency), and $y$ the response. The common solution method is to factorize $X$ as either its QR decomposition or Cholesky decomposition. Singular value decomposition may also be used, but it is rare as the computational complexity is significantly higher. In the case of the QR decomposition the solution method comes down to, transforming the model matrix and the response by row-wise multiplying them by the square root of the weights. Afterwards, the factorization is used to solve the system of equations using the appropriate method. In the case of a QR decomposition, $R$ is an upper triangular matrix which enables back substitution to obtain the solution efficiently without matrix inversion. However, a Cholesky decomposition would still be required if the information matrix is desired. The solution method with QR decomposition is delineated in equation \ref{QR}.\footnote{The \textbackslash refers multiplication of $b$ by the inverse of $A$ on the left}

The case for the Cholesky decomposition follows closely and without loss of generality other variants could be used such as Bunch-Kaufman decomposition or the upper triangular form ($U^{\top}U$). The QR decomposition is more numerically stable, but more expensive than Cholesky.\footnote{$\mathcal{O}\left(n^{3}\right) > \mathcal{O}\left(2mn^{2}-\frac{2}{3}2n^{3}\right)$ where the matrix has $m$ rows and $n$ columns}. Equation \ref{Cholesky} delineates the solution method with Cholesky decomposition. Since the information matrix is an important component, Bunch-Kaufman decomposition, a Cholesky variant, is the preferred method used in \textit{Econometrics.jl}.

\begin{equation}
\label{QR}
\begin{split}
	\tilde{X} = X .* \sqrt{w} \\
	\tilde{y} = y .* \sqrt{w} \\
	QR = \tilde{X} \\
	\beta = R \ \backslash \ \left( Q^{\top} \tilde{y} \right)
\end{split}
\end{equation}

\begin{equation}
\label{Cholesky}
\begin{split}
	LL = \left( X^{\top} W X \right) \\
	\beta = L \ \backslash \ \left( X^{\top} W y \right) \\
	\Psi = \left( L^{-1}\right)^{\top} L^{-1}
\end{split}
\end{equation}

The remaining estimators will assume a Cholesky decomposition as part of the estimation technique. The QR decomposition will be used in models estimated through iterative reweighted least squares (IRLS) as the factorization may be computed once and recycled.

\subsection{Within Estimator}

The within estimator is an application of the Frisch-Waugh-Lovell theorem \cite{FWL, FWLProof}. The estimator allows to compute the parameters estimates and information matrix for a subset of predictors without having to include the full set of categorical features. For example, one may include individual fixed effects in a large data set that may increase the dimension of the model matrix to several thousand making the problem unfeasible or inefficient. Moreover, some parameters may not be consistently estimated in certain contexts. For example, individual fixed effects are not consistently estimated when there is a fixed length for the panels (i.e., more observations implies more parameters).

Consider the following model,
\begin{equation}
	y = X \beta + D \theta + e
\end{equation}
where $y$ is the response, $\beta$ the parameters of interest, $X$ the features of the parameters of interest, $D$ a high dimensional representation of categorical features as control, $\theta$ the parameters on said covariates, and $e$ the error term. In order to obtain the parameter estimates $\beta$ and the associated information matrix, we can estimate an alternative specification.
\begin{equation}
	\tilde{y} = \tilde{X} \beta + e
\end{equation}
where $\tilde{X}$ and $\tilde{y}$ are obtained by using projections, such as the annihilator matrix (i.e., $I - X \left(X^{\top}W X\right)^{-1} X^{\top})$. There are several methods to obtain a suitable alternative regression and these are not unique. \cite{reghdfe} presents several approaches to solving these problem including specialized methods in certain applications. Some implementations include \textit{reghdfe}, Stata module, and Matthieu Gomez \textit{FixedEffectModels.jl} package. The two most common approaches are solving for the residuals through a sparse least-squares problems such as with LSMR \cite{LSMR} or using some variant for the method of alternating projections. The residuals approach tends to be more efficient, but degrades certain aspects of the model (e.g., no longer able to obtain the mean response). The method of alternating projections is able to preserve under certain conditions artifacts of the original regression such as obtaining the same estimate for the intercept even though it is not particularly meaningful.

\subsection{Between Estimator}

The between estimator estimates
\begin{equation}
	\tilde{y} = \tilde{X} \beta + e
\end{equation}

where the transformed model components are collapsed through some dimension through the mean function. For example, one approach to obtaining the error component for a random effects model is to use model statistics of the between estimator collapsing by panel. The weighted version of the model uses the observation weights to compute the weighted mean values and may use the weight fractions by the collapsing dimension as weights for the weighted least squares regression on the transformed model.

\subsection{Random Effects Model}

The random effects model relies in estimating the unobserved error components. Random effects requires a particular schema for the data which has a panel component and a temporal component. There are multiple approaches, but the most common one is the Swamy-Arora approach \cite{SwamyArora}. This estimator uses the mean squared residuals estimates (i.e., deviance divided by residual degrees of freedom) of the between and within models using the panel dimension as the collapsing / dimension to absorb. The error components are estimated as
\begin{equation}
\begin{split}
	\theta_{g} = 1 - \sqrt{\frac{\sigma_{e}^{2}}{T_{g} * \sigma_{u}^{2} + \sigma_{e}^{2}}} \\
	\sigma_{e}^{2} = W \\
	\sigma_{u}^{2} = \max\left\{0, B - \sigma_{e}^{2} * \bar{T}\right\} \\
\end{split}
\end{equation}

where $W$ is the mean squared residuals of the within model, $B$ the mean squared residuals of the between model, and $T_{g}$ is the length of the panel $g$, and $\bar{T}$ is the harmonic mean of the panel lengths.

The model terms are then transformed by partial demeaning
\begin{equation}
\begin{split}
\tilde{y}_{it} = y_{it} - \theta_{g} * \bar{y}_{.t} \\
\tilde{X}_{it} = X_{it} - \theta_{g} * \bar{X}_{.t}
\end{split}
\end{equation}

and these are used in the standard regression setting.

\subsection{First-Difference}

The first-difference estimator is a special case that use time / panel context for feature designs. The most common transformations include contrasts such as treatment coding (dummy coding), sum coding (effects coding) or Helmert coding which apply to categorical variables. Other common feature engineering techniques include log-transform and polynomial terms. However, certain transformations require a context such as a time dimension. Some examples include shift operations (lag, lead) and differentiating (e.g., first-difference). These operations may optionally require a group context such that the operations are performed group wise. Time-context operations have important concepts such as frequency and gaps. The frequency describes the difference between periods/observations and gaps describe observations that are skipped and should be understood as missing.

\subsection{Instrumental Variables}

Every estimator thus far can be generalized to include endogenous covariates through instrumental variables. The most common method is through two stages least squares (2SLS). The idea is to first apply all the relevant transformations to the model terms and apply the 2SLS standard procedure. In the case of the random effects model, the within and between models are estimated using 2SLS to obtain the error component estimates. After applying the random effects transformation to each model term the 2SLS process is employed in the final regression model à la \cite{BV_1987}.

The standard 2SLS estimator uses,
\begin{equation}
\begin{split}
\hat{z} = [X Z] \left[ \left( [X Z]^{\top} W [X Z] \right)^{-1} [X Z]^{\top} W z\ \right] \\
\hat{\beta} = \left( [X \hat{z}]^{\top} W [X \hat{z}] \right)^{-1} [X \hat{z}]^{\top} W y \\
\Psi = \left( [X \hat{z}]^{\top} W [X \hat{z}] \right)^{-1} \\
\hat{y} = [X z] \hat{\beta}
\end{split}
\end{equation}

for each model where $z$ is endogenous variables and $Z$ the additional instruments.

\subsection{Nominal Response Model}

Multinomial logistic regression is a probability model for estimating probabilities across multiple categories. It is a vector generalized linear model with softmax link function and the categorical distribution. It is estimated through iterative re-weighted least squares (IRLS) methods such as the QR Newton variant \cite{OLeary_1990}. The data schema for discrete choice models include the response (observed behavior), unit of observation covariates, and outcomes-specific covariates. The initial implementation allows for the base case of no-outcome specific features.

\subsection{Ordinal Response Model}

Ordinal logistic regression is a probability model for estimating probabilities across multiple ordered categories. Similarly to its nominal counterpart, it has a pool of alternatives, and observed outcome, unit of observation covariates, and outcome-specific covariates. A common assumption is the proportional odds assumption which may be relaxed in other models.

The log-likelihood function has the same form as the general form for computing the cost associated with a categorical distribution and predicted probability for realization. More specific,
\begin{equation}
	\ell \ell = \sum_{i = 1}^{m} \sum_{k}^{K} \mathbbm{1}\left(y_{i} = k\right) \ln\left[F\left(\alpha_{k + 1} - \eta\right) - F\left(\alpha_{k} - \eta\right)\right]
\end{equation}

where $F$ is the cumulative distribution function of the logistic distribution with zero location and unit scale, $\eta$ is the linear projection, and $\alpha_{k}$ is the threshold for lower threshold \cite{ologit}. The log-likelihood function and the gradient are passed to the \textit{Optim.jl} framework \cite{Optim} using \textit{ForwardDiff.jl} \cite{ForwardDiff} forward mode automatic differentiation (AD) for the Newtonian solver.

\subsection{Count/Rate Model}

Count/rate models are generalized linear models and follow a similar description as nominal models. The most common distribution choices are Poisson and Negative Binomial with the log link function. Negative Binomial is a generalization of the Poisson model, which adds an extra parameter for modeling the second moment (i.e., relaxes the mean equal variance assumption in the Poisson model). For the Negative Binomial to be a distribution in the exponential family it needs a restriction parameter which may be optimized through maximum likelihood estimation. An offset may be included to handle rates, a generalization of counts, that account for differences in exposures. Other generalizations include additive or multiplicative errors relations.

\subsection{Duration Models}

Duration models deal with responses of the type time until an event. One such model is the Cox proportional hazards model which relies on the proportional hazards assumption. Various models of these kind may be re-specified in a generalized linear model framework relating to the previous descriptions.

\section{Technical Challenges}

One technical challenge that is prevalent through every model is the issue of rank deficient terms. Rank deficient systems of linear equations are not identifiable. One approach is to error out and let the user explore and find a subset of features such that the no multi-collinearity assumption holds. The second approach is to automatically promote the system to a full rank version by excluding linearly dependent features. How much collinearity is too much is not an exact science. Some potential criteria include using the absolute values of the diagonal in the triangular matrix of the factorization (e.g., $L$ in $LL^{\top}$, $R$ in $QR$, $D$ in $LDL^{\top}$, $\Sigma$ in $U\Sigma V^{\top}$). These values are then compared against a chosen tolerance and the column of the term is deemed linearly independent if the values are greater than the tolerance. Note that Cholesky, QR, and Bunch-Kaufman decomposition allow to identify which columns are independent while singular values only allow to determine the rank. It may be arbitrary to choose among linearly dependent features. An additional level of complexity in probability models is the issue of linearly separability. \cite{Konis_2007} provides an overview of potential approaches to identifying the issue.

\section{Julia Ecosystem}

The usual pipeline for regression analysis involves (1) accessing data (I/O), (2) obtaining a tabular data representation, (3) data wrangling, and (4) employing regression analysis tools. The Julia ecosystem follows this canonical pipeline. The following sections provides an overview of the pipeline available in Julia.

\subsection{Data to Modeling}

\textit{StatsBase.jl} builds on top of Statistics.jl (standard library) to provide additional statistical functionality. One which includes the abstraction for Statistical Models (and Regression models which inherit from the former). It provides a simple and powerful API for the whole Julia ecosystem to use. It allows packages to implement the API and easily support a common functionality users can expect and interact with in a familiar manner. For example, \textit{coef} will extract the parameter estimates from any object that implements the API. The full API include model statistics such as: coefficient of determination (or adjusted), information criteria statistics such as AIC/BIC (and corrected), statistics about the model fitness such as deviance, log-likelihood, and usual queries such as point estimates, variance covariance estimates, standard errors, confidence intervals, degrees of freedom (or residual degrees of freedom), etc. Lastly, several accessors are available for fitted values, response, model matrix, information matrix, leverage values, error components, etc. Lastly, it also provides an abstraction for weights including frequency weights and analytical weights.

\textit{Tables.jl} provide an interface for tabular data. This API allows users to choose from various solutions the tabular data implementation of their choosing without having to worry that their choice will limit potential functionality. Many tabular implementations such as \textit{DataFrames.jl} provide robust functionality to many routines such as handling categorical features, dates/time, missing values, reshaping data, split/apply operations, and others. Users need not to worry about any I/O issues as a rich array of options exist for importing and exporting across different file formats such as delimiter-separated values, JSON, Feather, HDF5, MATLAB, Stata, SPSS, SAS, and R.

\textit{StatsModels.jl} is a package that provides the means to go from data to model terms. It provides the formulae language (e.g., similar syntax to R's formulae syntax). A model is then build using a formula, data, and additional model specific arguments. The process can be summarized as (1) collecting the information in the formula, (2) parsing its meaning by applying a schema based on the data, user-specified contrasts or other arguments, and (3) generating the model terms such as a response, model matrices, etc. Lastly, a package fits said model and implements the API.

\subsection{Regression Analysis}

The regression analysis ecosystem in Julia has \textit{GLM.jl} as its flagship. \textit{GLM.jl} provides the typical functionality for fitting generalized linear models through Fisher scoring. This includes linear models, Poisson/Negative Binomial, Logit/Probit, and other non-canonical link models. \textit{CovarianceMatrices.jl} provides various variance covariance estimators for \textit{GLM.jl} models à la R's \textit{sandwich} package. \textit{LinearMixedModels.jl} \cite{LinearMixedModels} extends \textit{GLM.jl} for mixed-effects models. \textit{FixedEffectModels.jl} provides fast estimation of linear models with instrumental variables and high dimensional categorical variables à la \textit{reghdfe}. \textit{Survival.jl} provides a series of estimators for duration models. Two major gaps in the ecosystem include estimating nominal and ordinal response models (i.e., discrete choice) with more than two alternatives and support for longitudinal estimators.

\section{Econometrics.jl}

\textit{Econometrics.jl} is a package for performing several common econometrics routines in the Julia language. It aims to provide the following functionality for two major gaps in the ecosystem, longitudinal estimators and discrete choice models. Developing the package has resulted in many contributions in the current ecosystem. However, the development of this package serves multiple purposes beyond the immediate effect. As the statistics ecosystem evolves and matures, \textit{Econometrics.jl} aims to serve as inspiration and an alternative to design decisions, standards, and option for user.

\subsection{Fitting Models}

This section will showcase some examples of using the package for various estimators. For each estimator a brief description of the data, model, syntax, and output will be provided. Results will be provided for Econometrics.jl and some alternatives such as R or Stata.

For linear models, the examples use the crime data set from \cite{Crime}. The data set is a balanced longitudinal data set with 90 counties in North Carolina from 1981 to 1987. The outcome variable is the crime rate and the explanatory variables include the probability of conviction, average sentence, and probability of prison sentence. Estimating the pooling estimator or between estimators can be accomplished as in figure \vref{estimator_pooling} and \vref{estimator_between}. Table \vref{poberes} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.

\begin{figure}[hbpt]
    \includegraphics[max width=\linewidth,center]{estimator_pooling}
	\caption{Estimation of the pooling estimator}
	\label{estimator_pooling}
\end{figure}

\begin{figure}[hbpt]
    \includegraphics[max width=\linewidth,center]{estimator_between}
	\caption{Estimation of the between panel estimator}
	\label{estimator_between}
\end{figure}

The fixed effects model or within estimator can be estimated as in figure \vref{withinmodel} which estimates the panel effects and the two-ways fixed effects model (i.e., fixed effects for time dimension as well). Table \vref{withinres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata, and R's plm package.

\begin{figure}[hbpt]
	\includegraphics[max width=\linewidth,center]{estimator_within}
	\caption{Estimation of the within estimator}
	\label{withinmodel}
\end{figure}

\begin{figure}[hbpt]
	\includegraphics[max width=\linewidth,center]{estimator_within2}
	\caption{Estimation of the within estimator with multiple fixed effects}
	\label{within2model}
\end{figure}

The random effects model can be estimated with similar syntax by including the \textit{PID} (panel identifier) and \textit{TID} (temporal identifier) tags such as in figure \vref{random} which shows estimating a random effects model as well as its instrumental variables counterpart. Table \vref{xtregres} shows the estimated 95\% confidence intervals using Econometrics.jl, Stata's reghdfe module, and R's plm package.

\begin{figure}[hbpt]
	\includegraphics[max width=\linewidth,center]{estimator_re}
	\caption{Estimation of the random effects model}
	\label{random}
\end{figure}

The sysdsn1 Stata example health insurance data set is used to illustrate the multinominal logistic regression when the response is nominal as seen in figure \vref{mlogit}. A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl and Stata is shown in table \vref{mlogitres}.

\begin{figure}[hbpt]
	\includegraphics[max width=\linewidth,center]{estimator_mlogit}
	\caption{Estimation of the multinomial logistic regression}
	\label{mlogit}
\end{figure}

The fullauto Stata example automobile models data set is used to illustrate the proportional ordinal logistic regression when the response is ordinal as seen in figure \vref{ologit}. A comparison with the estimates for the 95\% confidence intervals between Econometrics.jl, Stata, and R's MASS is shown in table \vref{ologitres}.

\begin{figure}[hbpt]
	\includegraphics[max width=\linewidth,center]{estimator_ologit}
	\caption{Estimation of the proportional odds logistic regression}
	\label{ologit}
\end{figure}

\subsection{Design Decisions}
